Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-04 main.tex
some annotations in last section

        \item 
		\mwl{Continue proof reading here.}
        We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
        \begin{align*}
            \Xi_{1} := \Psi \circ \Theta.
        \end{align*}
        It preserves the interface from $T$ onto $U$. 
		Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
        % We briefly recapitulate why it is bi-Lipschitz.
%         We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
%         We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
%         After application of a piecewise linear Lipschitz mapping, 
%         we can assume that $|\calK|$ is convex without loss of generality. 
%         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
%         By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipschitz. 
        The combination of the previous estimates for $\Psi$ and $\Theta$,
        as well as the upper bound $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$,
        provide 
        \begin{align*}
            \matnorm{ \Jacobian \Xi_{1} }
            &\leq 
            \Cfive{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}^{2}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            ,
            \\
            \matnorm{ \Jacobian \Xi_{1}^{-1} }
            &\leq  
            \Csechs{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            .
        \end{align*}
        We get the determinant estimates
        \begin{align*}
            |\det(\Xi_{1})|
            &\leq 
            \Cdetfive{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            B_{T}^{n}
            \aspectratio(\calT)^{n}
            ,
            \\
            |\det(\Xi_{1}^{-1})|
            &\leq 
            \Cdetsechs{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            \aspectratio(\calT)^{n}
            .
        \end{align*}
        This completes the desired estimates for $\Xi_{1}$.

@@

        We introduce a bi-Lipschitz mapping 
            \Psi : |\calR'| \rightarrow |\calK|
        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
            \frac{ \| A_{{G}}^{-1} x \|_{1} }{ \| A_{K}^{-1} x \|_{1} } x
        By the same line of thought, we see that it is invertible with inverse 
            \Psi^{-1}(x) 
            \frac{ \| A_{K}^{-1} x \|_{1} }{ \| A_{{G}}^{-1} x \|_{1} } x
        We analyze its Jacobian. 
        First, by assumption,
            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } x
        In what follows, $y \in \bbR^n$. We observe 
            \Jacobian \Psi(x) \cdot y 
            \frac{ 
                ( A_{{G}}^{-t} \vecone \cdot y ) 
                ( A_{K}^{-t} \vecone \cdot x )
                ( A_{{G}}^{-t} \vecone \cdot x )
                ( A_{K}^{-t} \vecone \cdot y ) 
            }{ 
                ( A_{K}^{-t} \vecone \cdot x )^2
            } 
            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } y
            \\&= 
            \frac{ 
                ( A_{{G}}^{-t} \vecone \cdot y ) 
            }{ 
                ( A_{K}^{-t} \vecone \cdot  x )
            } 
            \frac{ 
                ( A_{{G}}^{-t} \vecone \cdot x )
                ( A_{K}^{-t} \vecone \cdot y ) 
            }{ 
                ( A_{K}^{-t} \vecone \cdot  x )^2
            } 
            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } y
            \\&= 
            \frac{ 
                ( A_{{G}}^{-t} \vecone \cdot y ) 
            }{ 
                ( A_{K}^{-t} \vecone \cdot  x )
            } 
            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } 
                y
                \frac{ 
                    ( A_{K}^{-t} \vecone \cdot y ) 
                }{ 
                    ( A_{K}^{-t} \vecone \cdot  x ) 
                } 
        We see that the last summand is an oblique projection of $y$. 
        The vector $A_{K}^{-1} x$ has length at least $\sigma_{\min}( A_{K}^{-1} ) \| x \|$ and the product with $\vecone$ is smallest when the vector is colinear with one of the coordinate axes. We conclude that 
        \[
             A_{K}^{-t} \vecone \cdot x 
             \vecone \cdot A_{K}^{-1} x 
             \geq 
             \sigma_{\min}( A_{K}^{-1} ) \| x \|.
        \]
        Together with the Xu-Zikatanov inequality, we obtain the upper bound 
            \matnorm{ \Jacobian \Psi(x) }
            \sqrt{n}
            \frac{ \sigma_{\max}( A_{{G}}^{-1} ) }{ \sigma_{\min}( A_{K}^{-1} ) }
            n
            \frac{ \sigma_{\max}( A_{{G}}^{-1} ) \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{K}^{-2} ) }
        By completely analogous arguments, we find 
            \matnorm{ \Jacobian \Psi^{-1}(x) }
            \sqrt{n}
            \frac{ \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{{G}}^{-1} ) }
            n
            \frac{ \sigma_{\max}( A_{K}^{-1} ) \sigma_{\max}( A_{{G}}^{-1} ) }{ \sigma_{\min}( A_{{G}}^{-2} ) }
        It follows that 
            \Xi := \Psi \circ \Theta
        is a mapping from ${G}$ onto $U = \overline{\patch_{\calT}(S) \setminus {G}}$.
        It preserves the interface from ${G}$ onto $U$.

        \item 
        \color{red}
        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
        After application of a piecewise linear Lipschitz mapping, 
        we can assume that $|\calK|$ is convex without loss of generality. 
        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$.

        A similar argument applies to the triangulation $\calR'$. 
        We conclude that $\Xi$ is bi-Lipschitz. 
        \color{black}

        \item 
        \color{red}
        We collect several geometric facts.

        \item 
        We need to estimate the singular values of the transformation matrices within the bisected simplices. 
        Each bisection step reduces the diameter by at most a factor of one half,
        and it reduces the volume always by a factor of one half. 
        We use the estimates in Lemma~\ref{lemma:measurerelationships}.
        When $K \in \calK \cup \calS'r$, then 
        \begin{align*}
             \sigma_{\max}( A_{K}^{-1} )
             &\leq 
             \Czwei{n} \geometricshapemeasure(K) \diam(K)
             \leq 
             2 \Czwei{n} \geometricshapemeasure(\calT) \diam(K)^{-1}
             \\
             \sigma_{\min}( A_{K}^{-1} )^{-1}
             &= 
             \sigma_{\max}( A_{K} ) 
             \leq 
             \Ceins{n} \diam(K),
             \\ 
             \geometricshapemeasure( A_{K} )
             &\leq 
             \Cdrei{n} \geometricshapemeasure(K) \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
             .
        \end{align*}
        When ${G} \in \calR'$ is not our original simplex, then 
        \begin{align*}
             \sigma_{\max}( A_{{G}}^{-1} )
             &\leq 
             \Czwei{n} \geometricshapemeasure({G}) \diam({G})
             \leq 
             4 \Czwei{n} \geometricshapemeasure(\calT) \diam(G)^{-1},
             \\
             \sigma_{\min}( A_{{G}}^{-1} )^{-1}
             &= 
             \sigma_{\max}( A_{{G}} ) 
             \leq 
             \Ceins{n} \diam({G}),
             \\ 
             \geometricshapemeasure( A_{{G}} )
             &\leq 
             \Cdrei{n} \geometricshapemeasure({G}) \leq 4 \Cdrei{n} \geometricshapemeasure(\calT)
             .
        \end{align*}
        All the diameters above are comparable up to a factor of $\diameterratio(\calT)$.
        In summary,
        \begin{gather*}
            \matnorm{ \Jacobian \Theta_{|K}      } \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
            ,
            \qquad 
            \matnorm{ \Jacobian \Theta_{|K}^{-1} } \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
            ,
            \\
            \matnorm{ \Jacobian \Xi(x) }
            \leq 
            \sqrt{n}
            4 
            \geometricshapemeasure(\calT) 
            \Ceins{n} 
            \Czwei{n} 
            \diameterratio(\calT) % \frac{ \diam(K) }{ \diam(G) }
            \left( 
                1
                + 
                n
                2 \Cdrei{n} \geometricshapemeasure(\calT)
                4 
                \geometricshapemeasure(\calT) 
                \Ceins{n} 
                \Czwei{n} 
                \diameterratio(\calT) % \frac{ \diam(K) }{ \diam(G) }
            \right) 
            2 \Cdrei{n} \geometricshapemeasure(\calT)
            ,
            \\
            \matnorm{ \Jacobian \Xi^{-1}(x) }
            \leq 
            \sqrt{n}
            2 
            \geometricshapemeasure(\calT) 
            \Ceins{n} 
            \Czwei{n} 
            \diameterratio(\calT) % \frac{ \diam(G) }{ \diam(K) }
            \left( 
                1
                + 
                n
                2 \Cdrei{n} \geometricshapemeasure(\calT)
                2 
                \geometricshapemeasure(\calT) 
                \Ceins{n} 
                \Czwei{n} 
                \diameterratio(\calT) % \frac{ \diam(G) }{ \diam(K) }
            \right) 
            2 \Cdrei{n} \geometricshapemeasure(\calT)
            .
        \end{gather*}
\end{comment}

@@

We are now in the position to estimate Poincar\'e--Friedrichs constants for the exterior derivative over domains with shellable triangulations; this includes the curl and divergence operators in three dimensions. 
The estimates require local Poincar\'e--Friedrichs constants over simplices, 
with or without boundary conditions.

@@

\begin{lemma}\label{lemma:PFexteriorsimplex}
    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set. 
    Let $0 \leq k < n$. 
    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
    there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
    with $\cartan u = \cartan w$ and 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}
        &
        \leq 
        C_{{\PF},k,\Omega,p}
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    where 
    \begin{align*}
        C_{{\PF},k,\Omega,p} 
        = 
        n A_{\Poinc}(n,k+1) 
        \vol_{n}(B_1(0)) 
        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
        \diam(\Omega)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    This follows from the discussion in Section~\ref{section:potentialoperator}.
    This follows from Theorem~\ref{theorem:PF_EC} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{n}(B_1(0)) \diam(\Omega)^{n}$.
\end{proof}

@@

\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
    Let $T$ be an $n$-simplex 
    and let $F_{0},\dots,F_{\ell}$ be $\ell+1$ different faces of $T$. 
    Suppose that $u \in W^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq \ell$.
    Then there exists $w \in W^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} w = 0$ for $0 \leq i \leq \ell$
    and  
    \begin{align*}
        \cartan w = \cartan u,
        \quad 
        \| w \|_{L^{p}(\Omega)} 
        \leq 
        C_{\PF,\Gamma,\ell,k,p}(T)
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    Here, $C_{\PF,\Gamma,\ell,k,p}(T) > 0$ is a constant such that 
    \begin{align*}
        C_{\PF,\Gamma,\ell,k,p}(T)
        \leq 
        2^{\frac n p}
        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (\ell+1)/n! } 
        \algebraicshapemeasure(T)^{k-1}
        \Ceins{n}(T)^{k}
        \diam(T)^{k} 
        % \matnorm{\Jacobian \varphi}^{k}
        .
    \end{align*}
\end{lemma}
\todo{MV: There is indeed $\diam(T)^{k}$, with the power $k$? Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}. Moreover, so far, all the constants $C_{{\PF},T,p}$, $C_{{\PF},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\PF},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{section: PX_convex} have it outside. Finally, $\Omega$ in the indices is missing, whereas $l$ is superfluous. We should unify.}
\begin{proof}
    There exists $\varphi : \hat T \rightarrow T$ mapping the convex closure of the $n$ unit vectors onto the face $F_0$.
    We can also assume that the face of $\hat T$
    orthogonal to the $i$-th coordinate axis is mapped 
    onto the face $F_i$. 
    In what follows, we let $\tilde U$ be the domain obtained from reflecting $\hat T$ along the coordinate axes $l+1$ through $n$. 
    We see that $\vol(\tilde U) = (l+1)/n!$

    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in L^{p}(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
    Then $\cartan \hat u = \hat g$. 
    We let $\tilde u$ be the extension of $\hat u$ onto $\tilde U$ by reflection across the coordinate axes.
    We define $\tilde g = \cartan \tilde u$
    and see that $\tilde g$ is the extension of $\hat g$ onto $\tilde U$ by reflection across the coordinate axes. 
    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\tilde U)$.

    The bounds for the potential operators imply 
    the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\tilde U)$
    with $\cartan \tilde w = \cartan \tilde u$ and 
    \begin{align*}
        \| \tilde w \|_{L^{p}(\tilde U)}
        &\leq 
        n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_2(0)) }{ \vol(\tilde U) } 
        2
        \| \tilde g \|_{L^{p}(\tilde U)}
        \\&\leq 
        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
        \| \tilde g \|_{L^{p}(\tilde U)}
        .
    \end{align*}
    We let $w \in W^{p}\Lambda^{k}(T)$ be defined by $w := \varphi^{-\ast} \tilde w$.
    By construction, $\cartan w = \cartan u$,
    and $w$ has vanishing trace along the faces $F_{0},\dots,F_{l}$.

    In addition to that, by Proposition~\ref{proposition:pullbackestimate}:
    \begin{align*}
        \| w \|_{L^{p}(T)}
        &\leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
        \| \tilde w \|_{L^{p}(\hat T)}
        \\&
        \leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
        \| \tilde w \|_{L^{p}(\tilde U)}
        ,
        \\
        \| \tilde g \|_{L^{p}(\tilde U)}
        &\leq 
        2^{\frac n p}
        \| \hat g \|_{L^{p}(\hat T)}
        \leq 
        2^{\frac n p}
        |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
        \matnorm{\Jacobian \varphi}^{k}
        \cdot 
        \| \cartan u \|_{L^{p}(T)}
        .
    \end{align*}
    \todo{MV: the norms of the Jacobians have to be fixed.}
    The second inequality follows.
    \todo{MV: Please a few more details.}
\end{proof}

Whenever $\calT$ is an $n$-dimensional triangulation, we use the abbreviation
\begin{align*}
    C_{\PF,\Gamma,k,p}(\calT) 
    :=
    \max\limits_{ \substack{ T \in \calT \\ \dim(T)=n \\ 0 \leq l \leq n } }
    C_{\PF,\Gamma,l,k,p}(T)
    .
\end{align*}
We settle the following notation for our main result. 
Suppose that an $n$-dimensional triangulation $\calT$ has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
For each $1 \leq m \leq M$, the interface of the new simplex to the previous intermediate triangulation is 
\begin{align*}
    \Gamma_{m} := T_{m} \cap \left( T_{0} \cup \dots \cup T_{m-1} \right)
\end{align*}
According to Lemma~\ref{lemma:existenceofstar}, 
there exists a simplex $S_{m} \in \calT$ 
such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $T_{m} \in \patch_{\calT}(S_{m})$.
In particular, $\patch_{\calT}(S_{m})$ is already included in the union of the simplices up to $T_m$. 
We write 
\begin{align*}
    \Minako_{m} := \patch_{\calT}(S_{m}) \setminus T_{m}.
\end{align*}
for the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m})$.

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable $n$-dimensional triangulation $\calT$.
    Let $T_0, T_1, \dots, T_M$ be a shelling.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
    and such that for each $T_{m} \in \calT$, $1 \leq m \leq M$, in the shelling
    we have the following recursive estimate: 
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
        &
        \leq  
        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
        \diam(T)^{k} 
        \left( 
            \| \cartan u      \|_{L^{p}(T_{m})} 
            +
            \Cfive{n}{k}(\calT)^{k+1} 
            \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
            \| \cartan u \|_{L^{p}(\Minako_{m-1})}
        \right)
        \\&\qquad
        + 
        \Cfive{n}{k}(\calT)^{k} 
        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(\Minako_{m-1})}
        .
    \end{align*}
    \mwl{The notation $\Minako_m$ should be settled in the definition of shellings.}
\end{theorem}
\begin{proof}
    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
    By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
    We write $X_m := \cup_{j=0}^{m} T_j$, which is a triangulated $n$-dimensional submanifold with boundary.

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with an $n$-dimensional shellable triangulation $\calT$.
    Let $T_0, T_1, \dots, T_M$ be a shelling.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
    such that 
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
        \leq 
        C_{\PF,T,k,p}(T_{0})
        \prod_{i=0}^{m} 
        C_{???}
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
\end{theorem}
\begin{proof}
    We prove this via induction. 
    The statement is clearly satisfied when $m=0$ because then we only consider a single simplex. 
    Let us assume that the statement is true for some integer $m-1 \geq 0$.

>>>>

        \item 
		\mwl{Use interlacing inequalities.}
        We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
        \begin{align*}
            \Xi_{1} := \Psi \circ \Theta.
        \end{align*}
        It preserves the interface from $T$ onto $U$. 
		Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
        % We briefly recapitulate why it is bi-Lipschitz.
%         We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
%         We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
%         After application of a piecewise linear Lipschitz mapping, 
%         we can assume that $|\calK|$ is convex without loss of generality. 
%         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
%         By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipschitz. 
        The combination of the previous estimates for $\Psi$ and $\Theta$,
        as well as the upper bound $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$,
        provide 
        \begin{align*}
            \matnorm{ \Jacobian \Xi_{1} }
            &\leq 
            \Cfive{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}^{2}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            ,
            \\
            \matnorm{ \Jacobian \Xi_{1}^{-1} }
            &\leq  
            \Csechs{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            .
        \end{align*}
        We get the determinant estimates
        \begin{align*}
            |\det(\Xi_{1})|
            &\leq 
            \Cdetfive{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            B_{T}^{n}
            \aspectratio(\calT)^{n}
            ,
            \\
            |\det(\Xi_{1}^{-1})|
            &\leq 
            \Cdetsechs{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            \aspectratio(\calT)^{n}
            .
        \end{align*}
        This completes the desired estimates for $\Xi_{1}$.

@@

@@

We are now in the position to develop Poincar\'e--Friedrichs constants for the exterior derivative over domains with shellable triangulations; this includes the curl and divergence operators in three dimensions. 
These results use local Poincar\'e--Friedrichs constants over simplices, 
with or without boundary conditions, as subcomponents.

@@

\begin{lemma}\label{lemma:PFexteriorsimplex}
    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set. 
    Let $0 \leq k < n$. 
    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
    there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
    with $\cartan u = \cartan w$ and 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}
        &
        \leq 
        C_{{\PF},k,\Omega,p}
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    where 
    \begin{align*}
        C_{{\PF},k,\Omega,p} 
        = 
        n A_{\Poinc}(n,k+1) 
        \vol_{n}(B_1(0)) 
        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
        \diam(\Omega)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    This follows from the discussion in Section~\ref{section:potentialoperator}.
    This follows from Theorem~\ref{theorem:PF_EC} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{n}(B_1(0)) \diam(\Omega)^{n}$.
	\mwl{check final form of result}
\end{proof}

@@

\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
    Let $T$ be an $n$-simplex 
    and let $F_{0},\dots,F_{\ell}$ be $\ell+1$ different faces of $T$. 
    Suppose that $u \in W^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq \ell$.
    Then there exists $w \in W^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} w = 0$ for $0 \leq i \leq \ell$
    and  
    \begin{align*}
        \cartan w = \cartan u,
        \quad 
        \| w \|_{L^{p}(\Omega)} 
        \leq 
        C_{\PF,\Gamma,\ell,k,p}(T)
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    Here, $C_{\PF,\Gamma,\ell,k,p}(T) > 0$ is a constant such that 
    \begin{align*}
        C_{\PF,\Gamma,\ell,k,p}(T)
        \leq 
        2^{\frac n p}
        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (\ell+1)/n! } 
        \algebraicshapemeasure(T)^{k-1}
        \Ceins{n}(T)^{k}
        \diam(T)
        % \matnorm{\Jacobian \varphi}^{k}
        .
    \end{align*}
\end{lemma}
\mwl{MV: There is indeed $\diam(T)^{k}$, with the power $k$? Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}. Moreover, so far, all the constants $C_{{\PF},T,p}$, $C_{{\PF},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\PF},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{section: PX_convex} have it outside. Finally, $\Omega$ in the indices is missing, whereas $l$ is superfluous. We should unify.}
\begin{proof}
    There exists an affine bijection $\varphi : \hat T \rightarrow T$ 
	that maps the convex closure of the $n$ unit vectors onto the face $F_0$.
    We can also assume that the face of $\hat T$
    orthogonal to the $i$-th coordinate axis is mapped 
    onto the face $F_i$. 
    In what follows, we let $\tilde U$ be the domain obtained from reflecting $\hat T$ along the coordinate axes $l+1$ through $n$. 
    We see that $\vol(\tilde U) = (l+1)/n!$

    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in L^{p}(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
    Then $\cartan \hat u = \hat g$. 
    We let $\tilde u$ be the extension of $\hat u$ onto $\tilde U$ by reflection across the coordinate axes,
    and let $\tilde g$ is the extension of $\hat g$ onto $\tilde U$ by reflection across the coordinate axes. 
    We observe $\tilde g = \cartan \tilde u$
    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\tilde U)$.

    The bounds for the Bogovski\u{i} potential operators, Theorem~\ref{theorem:...} imply 
    the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\tilde U)$
    with $\cartan \tilde w = \cartan \tilde u$ and 
    \begin{align*}
        \| \tilde w \|_{L^{p}(\tilde U)}
        &\leq 
        n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_2(0)) }{ \vol(\tilde U) } 
        2
        \| \tilde g \|_{L^{p}(\tilde U)}
        \\&\leq 
        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
        \| \tilde g \|_{L^{p}(\tilde U)}
        .
    \end{align*}
    We let $w \in W^{p}\Lambda^{k}(T)$ be defined by $w := \varphi^{-\ast} ( \tilde w_{|\hat T} )$.
    By construction, $\cartan w = \cartan u$,
    and $w$ has vanishing trace along the faces $F_{0},\dots,F_{l}$.

    In addition to that, by Proposition~\ref{proposition:pullbackestimate}:
    \begin{align*}
        \| w \|_{L^{p}(T)}
        &\leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
        \| \tilde w \|_{L^{p}(\hat T)}
        ,
        \\
        \| \tilde g \|_{L^{p}(\tilde U)}
        &\leq 
        2^{\frac {n-\ell} p}
        \| \hat g \|_{L^{p}(\hat T)}
        \leq 
        2^{\frac {n-\ell} p}
        |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
        \matnorm{\Jacobian \varphi}^{k}
        \cdot 
        \| \cartan u \|_{L^{p}(T)}
        .
    \end{align*}
    It remains to use Lemma~\ref{lemma:measurerelationships}, and the desired inequality is shown. \mwl{Double check result}
\end{proof}

We settle the following notation for our main result. 
Whenever $\calT$ is an $n$-dimensional triangulation, we use the abbreviation
\begin{align*}
    C_{\PF,\Gamma,k,p}(\calT) 
    :=
    \max\limits_{ \substack{ T \in \calT \\ \dim(T)=n \\ 0 \leq l \leq n } }
    C_{\PF,\Gamma,l,k,p}(T)
    .
\end{align*}
Suppose that an $n$-dimensional triangulation $\calT$ has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
\begin{align*}
    \mwl{X_{m} := ...}
\end{align*}
For each $1 \leq m \leq M$, the interface of the new simplex to the previous intermediate triangulation is 
\begin{align*}
    \Gamma_{m} := T_{m} \cap \left( T_{0} \cup \dots \cup T_{m-1} \right)
\end{align*}
According to Lemma~\ref{lemma:existenceofstar}, 
there exists a simplex $S_{m} \in \calT$ 
such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $T_{m} \in \patch_{\calT}(S_{m})$.
In particular, $\patch_{\calT}(S_{m})$ is already included in the union of the simplices up to $T_m$. 
We write 
\begin{align*}
    \Minako_{m} := \patch_{\calT}(S_{m}) \setminus T_{m}.
\end{align*}
for the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m})$.

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable $n$-dimensional triangulation $\calT$.
    Let $T_0, T_1, \dots, T_M$ be a shelling.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
    and such that for each $T_{m} \in \calT$, $1 \leq m \leq M$, in the shelling
    we have the following recursive estimate: 
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
        &
        \leq  
        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
        \left( 
            \| \cartan u      \|_{L^{p}(T_{m})} 
            +
            \Cfive{n}{k}(\calT)^{k+1} 
            \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
            \| \cartan u \|_{L^{p}(\Minako_{m-1})}
        \right)
        \\&\qquad
        + 
        \Cfive{n}{k}(\calT)^{k} 
        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(\Minako_{m-1})}
        .
    \end{align*}
    \mwl{The notation $\Minako_m$ should be settled in the definition of shellings.}
\end{theorem}
\begin{proof}
    \mwl{Complete the proof.}
    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
    By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
    We write $X_m := \cup_{j=0}^{m} T_j$, which is a triangulated $n$-dimensional submanifold with boundary.

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with an $n$-dimensional shellable triangulation $\calT$.
    Let $T_0, T_1, \dots, T_M$ be a shelling.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
    such that 
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
        \leq 
        C_{\PF,T,k,p}(T_{0})
        \prod_{i=1}^{m} 
        C_{???}
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
\end{theorem}
\begin{proof}
    We prove this via induction. 
    The statement is clearly satisfied when $m=0$ because then we only consider a single simplex. 
    Let us assume that the statement is true for some integer $m-1 \geq 0$.
